Brief Announcement: Tight Bounds for Online Balanced Repartitioning

### 2020-03-27 paper/paper.tex
Rewrite

\maciek{TODO: a figure of 3 sets split.}

@@

\begin{proof}
We partition nodes into $3$ sets $A$, $B$, and $C$.
Sets have cardinalities $|A| = k-1$, $|B| = k-1$, and $|C| = 2$.
Each element $e$ of the universe $U$ have a corresponding node $v_e \in A\cup B\cup C$.

@@

Now we bound the costs of the algorithm for any sequence of paging requests transformed the way described above.
For any request, the algorithm pays $0$ if it has $S$ collocated, and otherwise it pays at least $2\alpha$ for at least one migration needed to achieve state where $S$ is collocated.

Now we construct an offline algorithm OPT.
OPT only resides in three types of configurations:
\begin{enumerate}
  \item With set $A$ collocated in one cluster, set $B$ collocated in the other, and set $B$ having one node in one cluster and the other node in the second
  \item With set $A$ collocated in one cluster, with a single node from set $B$; on the second cluster, we have both nodes from set $C$, and $k-2$ nodes from set $B$
  \item the symmetric configuration to the previous one, with set $A$ split, and sets $B$ and $C$ collocated
\end{enumerate}
To transition between any of these configuration types, a single exchange is needed, hence OPT pays $2\alpha$ for it.
Within each type of configuration, OPT may exchange the split node with any node from his set for $2\alpha$.

>>>>

\maciek{TODO: example figure of 3 sets split. Example figure of three states of OPT}

@@

\begin{proof}
We partition nodes into $3$ sets $A$, $B$, and $C$.
Sets have cardinalities $|A| = k-1$, $|B| = k-1$, and $|C| = 2$.
Each element $e$ of the universe $U$ have a corresponding node $v_e \in A\cup B\cup C$.
\maciek{define that A,B,C is collocated/split}

@@

Now we lower-bound the cost of the algorithm for any sequence of pairwise requests that were produced by the described transformation of paging requests.
For any such request, the algorithm pays $0$ if it has $S$ collocated, and otherwise it pays at least $2\alpha$ for at least one migration needed to reach the state with $S$ collocated.

We construct the following offline algorithm OPT.
OPT only resides in three types of configurations with respect to sets $A,B,C$ (cf. Figure TODO).
Without loss of generality, we describe the contents of clusters $X$ and $Y$:
\begin{enumerate}
  \item In $X$ we have $A$ and one node from $C$; in $Y$ we have $B$ and the other node from $C$.
  \item In $X$ we have $A$ and one node from $B$; in $Y$ we have $C$ and $k-2$ nodes from set $B$.
  \item In $X$ we have $B$ and one node from $A$; in $Y$ we have $C$ and $k-2$ nodes from set $A$.
\end{enumerate}

Now we describe the possible actions performed by OPT.
Within each type of configuration with $S \in \{ A, B, C\}$ split, OPT may exchange the split node with any node from $S$.
To transition between any of three configuration types, it suffices to perform a single exchange.
Hence, for every action OPT pays $2\alpha$.
